---
title: "Lab1"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Lab1}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(Lab1Intro)
```

## Links

[Here](https://github.com/coxjohn/Lab1Intro) is a link to the Github repository containing this package, Lab1Intro.
You can find documentation for making packages in R here: <http://r-pkgs.had.co.nz/>.

## $\LaTeX$ formulae
Sample mean:
$$\bar{x}_{k} = \frac{1}{n}\sum_{j=1}^{n}x_{jk}\qquad k = 1,2,...,p\qquad(1-1)$$
Sample covariance:
$$s_{ik} = \frac{1}{n}\sum_{j=1}^{n}(x_{ji}-\bar{x}_{i})(x_{jk} - \bar{x}_{k})\qquad i=1,2,...,p\quad k=1,2,...,p\qquad (1-4)$$

Sample correlation coefficients:
$$r_{ik} = \frac{s_{ik}}{\sqrt{s_{ii}}\sqrt{s_{kk}}}=\frac{\sum_{j=1}^{n}(x_{ji}-\bar{x}_{i})(x_{jk} - \bar{x}_{k})}{\sqrt{\sum^{n}_{j=1}(x_{ji}-\bar{x}_{i})^2}\sqrt{\sum^{n}_{j=1}(x_{jk}-\bar{x}_{k})^2}}\qquad(1-5)$$
Sample covariance matrix:
$$\textbf{S}=\frac{1}{1-n}\textbf{X}'\Big(\textbf{I}-\frac{1}{n}\textbf{11}'\Big)\textbf{X}\qquad (3-27)$$
Sample standard deviation matrix:
$$\textbf{D}_{(p\times p)}^{1/2} = \begin{bmatrix}
                                    \sqrt{s_{11}} & 0 & \cdots & 0\\
                                    0 & \sqrt{s_{22}} & \cdots & 0\\
                                    \vdots & \vdots & \ddots & \vdots\\
                                    0 & 0 & \cdots & \sqrt{s_{pp}}
\end{bmatrix}\qquad (3-28)$$
Sample correlation matrix:
$$\textbf{R}=\textbf{D}^{-1/2}\textbf{SD}^{-1/2}\qquad (3-29)$$


## Paper mill data
Here is an analysis of the data from Table 1-2 from a paper mill using the functions created for this lab:
```{r}
data = read.table("T1-2.DAT");

sampmean(data)
sampcov(data, c("Density", "Strength(MD)", "Strength(CD)"))
sampcor(data, c("Density", "Strength(MD)", "Strength(CD)"))
```


## Assessment
The assessment for this course differs between 4793 and 5793. The assessment for 4793 is as follows:

* Clicker quiz each class and lab - 10%
* 4 Assignments - 20%
* Laboratories - 10%
* 2 Exams - 20%
* 2 Projects - 10%
* 1 final - 30%

For 5793:

* Clicker quiz each class and lab    - 10%
* 4 Assignments                      - 20%
* Laboratories                       - 10%
* 2 Exams                            - 20%
* 3 Projects (more weight on third)  - 10%
* 1 final                            - 30%

The only difference between the two is that there is an additional project for 5793, with more weight placed on the third project than the other two.
